Ecological validity of detecting data fabrication in experimental studies.

### 2016-05-30 submission/manuscript.Rmd
APS2016 talk commit

```{r prepwork, echo = FALSE}
VsuppressPackageStartupMessages(if(!require(pROC)){install.packages('pROC')})
suppressPackageStartupMessages(library(pROC))
suppressPackageStartupMessages(if(!require(foreign)){install.packages('foreign')})
suppressPackageStartupMessages(library(foreign))

@@

# Compute the summary statistics for Many Labs
source(sprintf('%sfunctions/compute_summary_anch_ml.R', x12))
# Process the collected, fabricated data
source(sprintf('%sfunctions/process_qualtrics_anch_01.R', x12))
# Concatenate, analyze, and write out all ML and qualtrics data
# Uncomment this line to rerun
set.seed(123);source(sprintf('%sfunctions/concatenate_analyze_01.R', x12))

@@

### Results.
```{r inspect results to detect data fabrication, echo = FALSE}

dat_summary <- read.csv(dat_summary_file)

tp <- NULL
fp <- NULL
fn <- NULL
tn <- NULL

i <- 1

for (threshold in seq(0, .1, .01))
{
  tp[i] <- sum(dat_summary$fish_combine_6_p < threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
  fp[i] <- sum(dat_summary$fish_combine_6_p < threshold & dat_summary$type == 'ml', na.rm = TRUE)
  fn[i] <- sum(dat_summary$fish_combine_6_p > threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
  tn[i] <- sum(dat_summary$fish_combine_6_p > threshold & dat_summary$type == 'ml', na.rm = TRUE)

@@

fpr <- fp / (fp + tn)
tpr <- tp / (tp + fp)
fnr <- fn / (fn + tp)
tnr <- tn / (tn + fn)
```

library(ROCR)
data(ROCR.simple)
pred <- prediction( ROCR.simple$predictions, ROCR.simple$labels)
perf <- performance(pred,"tpr","fpr")
plot(perf)
--->
# Study 2

>>>>

```{r prepwork, echo = FALSE}
suppressPackageStartupMessages(if(!require(pROC)){install.packages('pROC')})
suppressPackageStartupMessages(library(pROC))
suppressPackageStartupMessages(if(!require(foreign)){install.packages('foreign')})
suppressPackageStartupMessages(library(foreign))

@@

# Compute the summary statistics for Many Labs
source(sprintf('%sfunctions/compute_summary_anch_ml.R', x12))
# Process the collected, fabricated data
source(sprintf('%sfunctions/process_qualtrics_anch_01.R', x12))
# Concatenate, analyze, and write out all ML and qualtrics data
# Uncomment this line to rerun
# set.seed(123);source(sprintf('%sfunctions/concatenate_analyze_01.R', x12))

@@

### Results.
```{r inspect results to detect data fabrication, echo = FALSE}
# Read in datafile, just in case the computations were not re-run.
dat_summary <- read.csv(dat_summary_file)
dat_summary <- dat_summary[!(dat_summary$type == 'qualtrics' & is.na(dat_summary$bonus)), ]
# Select only those from qualtrics who did for bonus

type_index <- which(names(dat_summary) == 'type')

temp <- dat_summary[, c(type_index, 18:45)]

# ggplot(temp) +
#   facet_grid ()
# geom_density(aes(Result, group = type, col = type)) + 
#   xlab(title_name)
# 
# p <- ggplot(temp)
# for (i in 18:45)
# {
#   temp <- dat_summary[, c(type_index, i)]  
#   title_name <- names(temp)[2]
#   names(temp)[2] <- 'Result'
#   
#   ggplot(temp) +
#     geom_density(aes(Result, group = type, col = type)) + 
#     xlab(title_name)
# }
# dev.off()

tp <- matrix(NA, ncol = 20, nrow = 101)
fp <- matrix(NA,ncol = 20, nrow = 101)
fn <- matrix(NA,ncol = 20, nrow = 101)
tn <- matrix(NA,ncol = 20, nrow = 101)

temp <- names(dat_summary)[c(18:31, 34, 37, 39, 41, 43, 45)]

j <- 1

for (variables in c(18:31, 34, 37, 39, 41, 43, 45))
{
  i <- 1

  for (threshold in seq(0, 1, .01))
  {
    tp[i,j] <- sum(dat_summary[, variables] <= threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
    fp[i,j] <- sum(dat_summary[, variables] <= threshold & dat_summary$type == 'ml', na.rm = TRUE)
    fn[i,j] <- sum(dat_summary[, variables] > threshold & dat_summary$type == 'qualtrics', na.rm = TRUE)
    tn[i,j] <- sum(dat_summary[, variables] > threshold & dat_summary$type == 'ml', na.rm = TRUE)

@@

  j <- j + 1
}

# loop through matrix for proper comps

for (i in 1:20)
{
  tpr[, i] <- tp[, i] / (tp[, i] + fn[, i])
  fnr[, i] <- fn[, i] / (tp[, i] + fn[, i])
  fpr[, i] <- fp[, i] / (fp[, i] + tn[, i])
  tnr[, i] <- tn[, i] / (fp[, i] + tn[, i])

  ppv[, i] <- tp[, i] / (fp[, i] + tp[, i])
  fdr[, i] <- fp[, i] / (fp[, i] + tp[, i])
  npv[, i] <- tn[, i] / (tn[, i] + fn[, i])
  false_or[, i] <- fn[, i] / (tn[, i] + fn[, i])
}
fpr <- as.data.frame(fpr)
tpr <- as.data.frame(tpr)
fnr <- as.data.frame(fnr)
tnr <- as.data.frame(tnr)

ppv <- as.data.frame(ppv)
fdr <- as.data.frame(fdr)
npv <- as.data.frame(npv)
false_or <- as.data.frame(false_or)

names(fpr) <- temp
names(tpr) <- temp
names(fnr) <- temp
names(tnr) <- temp

names(ppv) <- temp
names(fdr) <- temp
names(npv) <- temp
names(false_or) <- temp

for(i in 1:20)
{
  plot(fpr[, i], tpr[, i],
       type = 's', xlim = c(0,1), ylim = c(0,1), main = names(fpr)[i],
       xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2)
  abline(a = 0, b = 1)
}

tp[6,which(temp == 'fish_combine_3_hetero_p')]
fp[6,which(temp == 'fish_combine_3_hetero_p')]
fn[6,which(temp == 'fish_combine_3_hetero_p')]
tn[6,which(temp == 'fish_combine_3_hetero_p')]

plot(fpr$fish_combine_3_hetero_p, tpr$fish_combine_3_hetero_p,
     type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Fisher combined',
     xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2)
abline(a = 0, b = 1)
roc(response = dat_summary$type, predictor = dat_summary$fish_combine_3_hetero_p)

height = (tpr$fish_combine_3_hetero_p[-1]+tpr$fish_combine_3_hetero_p[-length(tpr$fish_combine_3_hetero_p)])/2
width = diff(fpr$fish_combine_3_hetero_p) # = diff(rev(omspec))
sum(height*width)

plot(fpr$variance_sd_p_overall_homo, tpr$variance_sd_p_overall_homo,
     type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance homogeneous',
     xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2)
abline(a = 0, b = 1)
roc(response = dat_summary$type, predictor = dat_summary$variance_sd_p_overall_homo)

height = (tpr$variance_sd_p_overall_homo[-1]+tpr$variance_sd_p_overall_homo[-length(tpr$variance_sd_p_overall_homo)])/2
width = diff(fpr$variance_sd_p_overall_homo) # = diff(rev(omspec))
sum(height*width)

plot(fpr$variance_sd_p_overall_hetero, tpr$variance_sd_p_overall_hetero,
     type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance heterogeneous',
     xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2)
abline(a = 0, b = 1)
roc(response = dat_summary$type, predictor = dat_summary$variance_sd_p_overall_hetero)

height = (tpr$variance_sd_p_overall_hetero[-1]+tpr$variance_sd_p_overall_hetero[-length(tpr$variance_sd_p_overall_hetero)])/2
width = diff(fpr$variance_sd_p_overall_hetero) # = diff(rev(omspec))
sum(height*width)

plot(fpr$variance_sd_p_overall_homo, tpr$variance_sd_p_overall_homo,
     type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance homogeneous',
     xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2)
abline(a = 0, b = 1)
lines(fpr$variance_sd_p_overall_hetero, tpr$variance_sd_p_overall_hetero,
     type = 's', xlim = c(0,1), ylim = c(0,1), main = 'Variance heterogeneous',
     xlab = 'Sensitivity / TPR', ylab = 'Specificity / TNR', lwd = 2, lty = 2)

legend(x = 0, y = 1, bty = 'n', lty = c(1, 2), lwd = 2, legend = c('Homogeneous', 'Heterogeneous'))

plot(x = roc(response = dat_summary$type,
             predictor = dat_summary$fish_combine_3_hetero_p,
             percent = TRUE,
             ci = TRUE,
             of = 'se',
             sp = seq(0, 100, 5)), ci.type="shape")

plot(x = roc(response = dat_summary$type,
             predictor = dat_summary$variance_sd_p_overall_homo,
             percent = TRUE,
             ci = TRUE,
             of = 'se',
             sp = seq(0, 100, 5)), ci.type="shape")

for (i in c(18,23))
{
  plot(x = roc(response = dat_summary$type,
               predictor = dat_summary[, i],
               percent = TRUE,
               ci = TRUE,
               of = 'se',
               sp = seq(0, 100, 5)), ci.type="shape", main = names(dat_summary)[i])
}

plot(fpr[,1], tpr[,1], type = 's')
lines(fpr[,6], tpr[,6], type = 's')

plot(x = roc(response = dat_summary$type,
             predictor = dat_summary$variance_sd_p_overall_homo,
             percent = TRUE,
             ci = TRUE,
             of = 'se',
             sp = seq(0, 100, 5)), ci.type="shape", main = 'homogeneous')
plot(x = fpr$variance_sd_p_overall_homo, y = tpr$variance_sd_p_overall_homo, type = 's')

plot(x = roc(response = dat_summary$type,
             predictor = dat_summary$variance_sd_p_overall_hetero,
             percent = TRUE,
             ci = TRUE,
             of = 'se',
             sp = seq(0, 100, 5)), ci.type="shape", main = 'homogeneous')
plot(x = fpr$variance_sd_p_overall_hetero, y = tpr$variance_sd_p_overall_hetero, type = 's')
```

# Study 2
